Data Appendix to \"The impact of weather events on schooling outcomes\

### 2020-04-05 data_appendix_all_years.Rmd
Used case_when instead of recode to recode the reason variable.

hh_2005 <- data_2005 %>% 
  select(hh_id, assist, reason, members, sex, age,
         relation, literacy, register, grade, repeated, depto, urb_rur, income) %>% 
  mutate(year = 2005,
         hh_id = as.numeric(hh_id),
         dept = case_when(depto == "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"))
```
```{r export summary table 2005}
export_summary_table(dfSummary(hh_2005))
```

>>>>

hh_2005 <- data_2005 %>% 
  select(hh_id, assist, reason, members, sex, age,
         relation, literacy, register, grade, repeated, depto, urb_rur, income) %>% 
  mutate(year = 2005,
         hh_id = as.numeric(hh_id),
         dept = case_when(depto == "1" ~ "Chuquisaca",
                          depto == "2" ~ "La Paz",
                          depto == "3" ~ "Cochabamba",
                          depto == "4" ~ "Oruro",
                          depto == "5" ~ "Potosi",
                          depto == "6" ~ "Tarija",
                          depto == "7" ~ "Santa Cruz",
                          depto == "8" ~ "Beni",
                          depto == "9" ~ "Pando"),
         reason = case_when(reason == 1 ~ 'vacation',
                            reason == 2 ~ 'money', 
                            reason == 3 ~ 'work',
                            reason == 4 ~ 'sickness/accident/disability',
                            reason == 5 ~ 'distance', 
                            reason == 6 ~ 'finished', 
                            reason == 7 ~ 'age',
                            reason == 8 ~ 'not interested',
                            reason == 9 ~ 'housework/childcare',
                            reason == 10 ~ 'other'))
```

Note: remove this section after reading it. I added the code for recoding the variable in the above section, but for learning purposes I wanted to tell you what the code you had does:

hh_2005 
prints the head of the hh_2005 data to the console but doesn't do anything with the data

reason <- as.factor(c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10))
creates a new object called reason that is a factor vector containing the numbers 1-10. But this line doesn't know that this is connected to the hh_2005 dataset. Notice that above, I used the pipe operator to tell R to take the dataset we had been working with and then recode a variable from that dataset

recode(reason, "1='vacation'; 2 = 'money'; 3 = 'work'; 4 = 'sickness/accident/disability'; 5 ='distance'; 6 = 'finished'; 7 = 'age'; 8 = 'not interested'; 9 = 'housework/childcare'; 10 = 'other'") 
returns an error because the list of reasons and numbers are one long character string that R can't parse and because the haven package creates objects that don't work with some of the R functions (like recode, apparently)

```{r export summary table 2005}
export_summary_table(dfSummary(hh_2005))
```
